Local Tuning in Peano curves-based global optimization scheme

### 2016-07-14 2016/YSC/ysc_paper.tex
Add title and links

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Local Tuning in }

@@

\titlerunning{Local Tuning in \ldots}

@@

The one-dimensional characteristic algorithms represent one of the classes of the
optimization algorithms used widely \cite{}. A number of schemes of reduction of the
multidimensional problems to one or several one-dimensional ones, i. e. the dimension
reduction schemes have been developed \cite{stronginBook}, \cite{butzCurves}.
\par
In recent years, when building the global optimization algorithms, an increased attention
is paid to accounting for the local properties of the optimized function. In the
case of the characteristic schemes, this approach allows developing a mixed algorithm
\cite{mixedAlg} as well as using different estimates of Lipschitz constant in different search
domain \cite{sergLocalTuningFirst}. Originally, the latter approach has been proposed for the one-dimensional
problems, also the investigation of this one when using the nested optimization scheme
has been carried out \cite{nestedLocal}. In all these cases, this approach have demonstrated itself to
be an efficient one, having allowed accelerating the convergence of the characteristic
optimization methods essentially. In the present paper, a generalization of the method
for building of the local estimates of Lipschitz constants onto the case of Hölder
functions obtained when reducing the multidimensional optimization problems is considered.

@@

The experiments on the evaluation of the efficiency of the method with the local
adaptive estimate of Hölder constant have been carried out using the two-dimensional
classes of Grishagin problems (\(F_{GR}\)) \cite{grishaginClass} and GKLS Simple 2d ones \cite{gklsClass}. Each class
includes 100 multiextremal functions. In all experiments, the evolvent was built
with the density \(m = 12\), parameter \(\varepsilon\) in the termination criterion was equal \(10^{-3}\).
The parameter \(r\) was selected as low as possible, which given method solves all
problems of the class at. The search step for \(r\) was \(0.1\).
\par
For clarity of illustration of the advantages of the local adaptive scheme of estimating
the constant \(H\), let us consider a particular example of the results obtained by the method.
In Fig. \ref{fig:grish_isolines}, the contour plots of a function from (\(F_{GR}\)) class and the trial
points executed by the method with the global estimate of Hölder constant and with
the one estimated according to formula (\ref{additiveConv}) are shown. As it is
seen from the figures, the method with global estimate of the constant executes a
large number of trials in the nearness of the global minimizer (total 1086 trials
have been executed) before the termination condition is satisfied, whereas the method
with the local adaptive estimate converges much faster (total 385 trials have been executed).
The same situation takes place when optimizing a function from GKLS Simple 2d class (Fig. \ref{fig:gkls_isolines}).
The method with the global estimate of the constant had executed 2600 trials while
the method with the local adaptive estimate had executed 1190 trials only.
\begin{figure}[ht]
    \centering
    \subfloat[global \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gs_glob.png} }}
    \qquad
    \subfloat[local-adaptive \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gs_loc.png} }}
    \caption{The contour plots of a function from (\(F_{GR}\)) class}
    \label{fig:grish_isolines}
\end{figure}

@@

%------------------------------------------------------------------------------
% Refs:
%
\label{sect:bib}
%\bibliographystyle{plain}
%\bibliographystyle{alpha}
\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\bibliography{ysc_paper}

>>>>

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Local Tuning in Peano curves-based global optimization scheme}

@@

\titlerunning{Local Tuning in Peano curves-based \ldots}

@@

The one-dimensional characteristic algorithms represent one of the classes of the
optimization algorithms used widely \cite{optHandbook}. A number of schemes of reduction of the
multidimensional problems to one or several one-dimensional ones, i. e. the dimension
reduction schemes have been developed \cite{stronginBook}, \cite{butzCurves}.
\par
In recent years, when building the global optimization algorithms, an increased attention
is paid to accounting for the local properties of the optimized function. In the
case of the characteristic schemes, this approach allows developing a mixed algorithm
\cite{mixedAlg} as well as using different estimates of Lipschitz constant in different search
domain \cite{sergLocalTuningFirst}. Originally, the latter approach has been proposed for the one-dimensional
problems, also the investigation of this one when using the nested optimization scheme
has been carried out \cite{nestedLocal}. In all these cases, this approach have demonstrated itself to
be an efficient one, having allowed accelerating the convergence of the characteristic
optimization methods essentially. In the present paper, a generalization of the method
for building of the local estimates of Lipschitz constants onto the case of Hölder
functions obtained when reducing the multidimensional optimization problems is considered.

@@

The experiments on the evaluation of the efficiency of the method with the local
adaptive estimate of Hölder constant have been carried out using the two-dimensional
classes of Grishagin problems (\(F_{GR}\)) \cite{grishaginClass} and GKLS Simple 2d ones \cite{gklsClass}. Each class
includes 100 multiextremal functions. In all experiments, the evolvent was built
with the density \(m = 12\), parameter \(\varepsilon\) in the termination criterion was equal \(10^{-3}\).
The parameter \(r\) was selected as low as possible, which given method solves all
problems of the class at. The search step for \(r\) was \(0.1\).
\par
For clarity of illustration of the advantages of the local adaptive scheme of estimating
the constant \(H\), let us consider a particular example of the results obtained by the method.
In Fig. \ref{fig:grish_isolines}, the contour plots of a function from \(F_{GR}\) class and the trial
points executed by the method with the global estimate of Hölder constant and with
the one estimated according to formula (\ref{additiveConv}) are shown. As it is
seen from the figures, the method with global estimate of the constant executes a
large number of trials in the nearness of the global minimizer (total 1086 trials
have been executed) before the termination condition is satisfied, whereas the method
with the local adaptive estimate converges much faster (total 385 trials have been executed).
The same situation takes place when optimizing a function from GKLS Simple 2d class (Fig. \ref{fig:gkls_isolines}).
The method with the global estimate of the constant had executed 2600 trials while
the method with the local adaptive estimate had executed 1190 trials only.
\begin{figure}[ht]
    \centering
    \subfloat[global \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gs_glob.png} }}
    \qquad
    \subfloat[local-adaptive \(H\) estimation]{{\includegraphics[width=0.45\textwidth]{images/gs_loc.png} }}
    \caption{The contour plots of a function from \(F_{GR}\) class}
    \label{fig:grish_isolines}
\end{figure}

@@

%------------------------------------------------------------------------------
% Refs:
%
\label{sect:bib}
\bibliographystyle{plain}
%\bibliographystyle{alpha}
%\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\bibliography{ysc_paper}
